Achieving maximum possible precision on stellar radial-velocity measurements in multi-epoch spectroscopy

### 2017-12-01 paper/paper.tex
CRLB text

The \CRLB\ is related to the Fisher Information that is frequently
used in cosmological experiment forecasts.

@@

In the case of \EPRV, this says that it is impossible to compute the
CRLB without making assumptions about the stellar spectrum (the
latent, unobserved, \emph{true} spectrum that could only be observed
with arbitrarily good data) and the noise processes that distort the
spectrum in any finite, noisy observation.

These noise processes necessarily must include any beliefs about
unsubtracted telluric absorptions or emissions, and time variability
of the star itself, not to mention photon and spectrograph read and
extraction noise.

The issue with

>>>>

@@

In particular, the \CRLB\ is related to the Fisher Information that is
frequently used in cosmological experiment forecasts (\todo{CITE
  SHIT}).
It is that the \emph{inverse variance} $\sigma_v^{-2}$ of any velocity
estimator must be larger than the second derivative of the
\emph{negative} log likelihood function.
In equations:
\begin{eqnarray}
\frac{1}{\sigma_v^2} &\geq& \frac{d^2}{d_v^2}(-\ln L)
\end{eqnarray}

In the case of \EPRV, this says that any computation of the limits
on estimating stellar velocities (or stellar velocity changes)
require making assumptions about the stellar spectrum (the
latent, unobserved, \emph{true} spectrum that could only be observed
with arbitrarily good data) and the noise processes that distort the
spectrum in any finite, noisy observation.
These noise processes ought (in principle) to include any beliefs about
unsubtracted telluric absorptions or emissions, and time variability
of the star itself, not to mention photon and spectrograph read and
extraction noise.
However---and in keeping with the literature---we can make maximal or
best-case assumptions, and ask what we would get for \EPRV\ precision
in that best case.
Then we can ask (with fake data) how much different choices about our
data analysis, and different adversarial injections of noise,
tellurics, spectrograph issues, and other wrongness can prevent us
from achieving the best-case bounds.

The most optimistic assumptions are... Gaussian... No
tellurics... perfect calibration... no time dependence... all
variances known...
